Hunting experience shapes individual foraging specialization and predator-prey interactions in an online videogame

### 2023-03-13 manuscript/Chapter2-manuscript.Rmd
update fig 2 caption. add notes MS

```{r fig2, out.width = "100%", fig.cap = "**Figure 2.** Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility. The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters."}

@@

Predators that experienced predictable encounters with their prey specialized in hunting at high speeds, while those that experienced more unpredictable encounters adopted a slower and flexible strategy. This is similar to other studies finding that fast-paced hunting is a highly specialized tactic suited for prey that use rapid escapes [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018;@Szopa-Comley.Ioannou2022]. On the contrary, instead of focusing solely on one tactic, predators that experienced unpredictable encounters probably adjusted their behaviour to minimize the consequences of uncertainty. Interestingly, both specialist and flexible hunters fine-tuned their tactic to their prey as they gained experience, suggesting that they learned how to hunt their prey. In that regard, our results provide direct evidence that the mechanism underlying the resource-predictability hypothesis may indeed involve predators learning to adjust their degree of specialization based on their prey [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017]. This is further supported by the fact that specialist and flexible hunters both achieved similar success throughout the study period. Therefore, our results have important implications for future predator-prey models, which should incorporate individual variation in learning and prey encounters to better predict under which ecological contexts specialization should be favoured over flexibility.

>>>>

```{r fig2, out.width = "100%", fig.cap = "**Figure 2.** Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility. The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters. Both figure panels are ordered by ascending degree of increase in either specialization or flexibility."}

@@

Predators that experienced predictable encounters with their prey specialized in hunting at high speeds, while those that experienced more unpredictable encounters adopted a slower and flexible strategy. This is similar to other studies finding that fast-paced hunting is a highly specialized tactic suited for prey that use rapid escapes [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018;@Szopa-Comley.Ioannou2022]. On the contrary, instead of focusing solely on one tactic, predators that experienced unpredictable encounters probably adjusted their behaviour to minimize the consequences of uncertainty. Interestingly, both specialist and flexible hunters fine-tuned their tactic to their prey as they gained experience, suggesting that they learned how to hunt their prey. In that regard, our results provide direct evidence that the mechanism underlying the resource-predictability hypothesis may indeed involve predators learning to adjust their degree of specialization based on their prey [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017]. This is further supported by the fact that specialist and flexible hunters both achieved similar success throughout the study period. Therefore, our results have important implications for future predator-prey models, which should incorporate individual variation in learning and prey encounters to better predict under which ecological contexts specialization should be favoured over flexibility. *important de faire ressortir que c'est seulement 10% des gens qui ont vraiment changé leur comportement de beaucoup. Ainsi ça va être + nuancé et me permettre de dire que certains ne répondent pas à l'expérience*.*affirmer que pt qu'ils répondent à d'autres expériences, mais que des contraintes logistiques nous empêchent de savoir quoi*
